---
title: "Cabbages"
author: "Racheal Adeneye"
date: "spring 2025"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

After looking at the variable, it looks like we have a numerical variable (how much vitamin C are in the crop) explained by a categorical variable (which of the two cultivation method was used). Those cultivation methods are called c39 and c52 methods.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
boxplot(VitC~Cult,data=veggy)
```

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

It seems as if Q1 of c52 is larger than Q3 of c39. This leads to a result that says they are statistically different.

### Numerical Descriptive Results

```{r}
favstats(VitC~Cult,data=veggy)
```

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Q1 of c39 is at 46 and Q1 of c52 is at 58. Both c39 and c52 have 30 numerical values in them.

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

The null hypothesis is there is no difference between these two methods of cultivation, c39 and c52, in reference to the amount of vitamin C in the cabbages. The probability of getting a result like this is 0.00000003405. Statistically, I reject the null hypothesis. The chances to get this result is exceedingly low as mentioned above. There is a big difference between the c39 and c52 methods, if you want a large amount of vitamin C in your cabbages, you should use the c52 method.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
First, we plotted the relationship between the VitC levels and the cultivation methods, c39 and c52, using a boxplot and described the results that we've seen. Then, we took a look at the numerical results and again wrote comments on what we seen. Lastly, we ran a t-test, stated our null hypothesis, found the probability, and ultimately rejected the null hypothesis because the probability was exceedingly small. Thus, we decided that the two cultivation methods are very different and that the c52 method produces a larger amount of vitamin C in the cabbages than thew c39 method.